Synthesizing Verified Components for Cyber Assured Systems Engineering \thanks{{DISTRIBUTION STATEMENT A. Approved for public release.} }

### 2021-05-15 paper/case-study.tex
Merge

In this section, we apply the BriefCASE tool to the development of a UAV surveillance system in which a UAV receives commands from a ground station to conduct surveillance along a geographical feature. The on-board mission computer then generates a flight plan consisting of a series of waypoints that the UAV must traverse to complete its mission. The UAV is also given a set of \textit{keep-in} and \textit{keep-out} zones that may constrain its flight path.

>>>>

In this section, we apply the BriefCASE tool to the development of a UAV surveillance system in which a UAV receives commands from a ground station to conduct surveillance over a geographical region. The on-board mission computer then generates a flight plan consisting of a series of waypoints that the UAV must traverse to complete its mission. The UAV is also given a set of \textit{keep-in} and \textit{keep-out} zones that may constrain its flight path.
